`r params$doc_title`

### 2022-11-18 scripts/MSc.Rmd
performance measures bias+mse

   # PERFORM MR_analysis
   mr.obj = MendelianRandomization::mr_input(
         bx = sim_dat$beta.bmi_sim_norm, 
         bxse = sim_dat$se_update_BMI, 
         # outcome
         by = sim_dat$beta.gbc_sim_norm, 
         byse = sim_dat$se_update_GBC, 
         snps = sim_dat$SNP,
         exposure = "Body mass index",
         outcome = "Gallbladder Cancer"
       ) 
   # CONMIX (as reference)
   res = MendelianRandomization::mr_conmix(mr.obj)
   colname_theta <- paste0("theta_sim_", n[i])
   colname_theta_se <- paste0("theta_se_sim_", n[i])
   ## store results
   est_sim[k, colname_theta] <- res$Estimate
   CIlength = res$CIUpper-res$CILower
   if (length(CIlength)>1) print("conmix multimodal")
   est_sim[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
   rm(res)
 }
 rm(se_update_BMI, se_update_GBC)
 print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}

@@

```{r}
bias <- function(thetaobs,theta) mean(thetaobs)- theta
mse <- function(thetaobs, theta) mean((thetaobs-theta)^2)

bias(thetaobs = est_sim$theta_sim_50000, theta = est$estimate[est$mr_methods == "conmix"])
mse(thetaobs = est_sim$theta_sim_50000, theta = est$estimate[est$mr_methods == "conmix"])
```

>>>>

   # PERFORM MR_analysis
   mr.obj = MendelianRandomization::mr_input(
         bx = sim_dat$beta.bmi_sim_norm, 
         bxse = sim_dat$se_update_BMI, 
         # outcome
         by = sim_dat$beta.gbc_sim_norm, 
         byse = sim_dat$se_update_GBC, 
         snps = sim_dat$SNP,
         exposure = "Body mass index",
         outcome = "Gallbladder Cancer"
       ) 
   # CONMIX (as reference)
   res = MendelianRandomization::mr_conmix(mr.obj)
   colname_theta <- paste0("theta_sim_", format(n[i], scientific=FALSE))
   colname_theta_se <- paste0("theta_se_sim_", format(n[i], scientific=FALSE))
   ## store results
   est_sim[k, colname_theta] <- res$Estimate
   CIlength = res$CIUpper-res$CILower
   if (length(CIlength)>1) print("conmix multimodal")
   est_sim[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
   rm(res)
 }
 rm(se_update_BMI, se_update_GBC)
 print(paste0("|||-----------------------Run finished for sample size: ", format(n[i], scientific=FALSE), " -----------------------|||"))
}

@@

```{r calculate-performance-metrics}
bias <- function(thetaobs,theta) mean(thetaobs)- theta
mse <- function(thetaobs, theta) mean((thetaobs-theta)^2)

colname_theta <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "theta_sim")]
colname_theta_se <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "theta_se_sim")]

# filter out sample sizes
sample_size_filtered <- as.numeric(str_extract(colname_theta, pattern = "(\\d)+"))

## get performance metrics
funs <- c(bias = bias, mse = mse)
args <- list(theta = est$estimate[est$mr_methods == "conmix"]) # trim argument non-matching and ignored for median

performance_metrics <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

```{r plot-performance-metrics}
#BIAS
ggplot(performance_metrics, aes(x=N, y=bias))+ 
  geom_point()

#MSE
ggplot(performance_metrics, aes(x=N, y=mse))+ 
  geom_point()

# compare distribution of simulated thetas against theta_324000
boxplot_dat <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim")

ggplot(boxplot_dat, aes(x=theta_sim, y=value))+
  geom_boxplot()+
  coord_flip()
